---
title: ASHG18 tweet summary day 5
author: L. Collado-Torres
date: '2018-10-20'
slug: ashg18-tweet-summary-day-5
categories:
  - Conference
tags:
  - ASHG
header:
  caption: ''
  image: ''
  preview: yes
---

```{r setup, echo = FALSE, message = FALSE, warning = FALSE}
## For R images to display well in the RSS feed (disable for local preview)
knitr::opts_knit$set(base.url = 'http://lcolladotor.github.io/post/')

## Load frequently used packages for blog posts
library('knitcitations') # for citations
library('BiocStyle') # for CRANpkg() Biocpkg() Githubpkg()
library('sessioninfo') # for session_info()

## Load knitcitations with a clean bibliography
cleanbib()
cite_options(hyperlink = 'to.doc', citation_format = 'text', style = 'html')

bib <- c(
    'BiocStyle' = citation('BiocStyle'),
    'blogdown' = citation('blogdown')[2],
    'knitcitations' = citation('knitcitations'),
    'sessioninfo' = citation('sessioninfo')
)
```


Continuing from my [ASHG18 day 1 post](http://lcolladotor.github.io/2018/10/16/ashg18-tweet-summary-day-1/#.W8gWEBNKg0o), [day 2](http://lcolladotor.github.io/2018/10/17/ashg18-tweet-summary-day-2/#.W8ggNxNKg0o), [day 3](http://lcolladotor.github.io/2018/10/18/ashg18-tweet-summary-day-3/#.W8mYLxNKg0o) and [day4](http://lcolladotor.github.io/2018/10/19/ashg18-tweet-summary-day-4/#.W8qdTRNKg0o) here's my list of tweets from day 5.

### 6C 9:15 am

#### Jane Loveland


`r blogdown::shortcode("tweet", user="ensembl", id="")`

`r blogdown::shortcode("tweet", user="dgmacarthur", id="")`

`r blogdown::shortcode("tweet", user="lcolladotor", id="")`

`r blogdown::shortcode("tweet", user="lcolladotor", id="")`

`r blogdown::shortcode("tweet", user="lcolladotor", id="")`



### 6B 10 am

#### Genevieve Stein-O’Brien

`r blogdown::shortcode("tweet", user="NeBanovich", id="")`

#### Yu Hu

`r blogdown::shortcode("tweet", user="lcolladotor", id="")`

Mingyao Li and Nancy Zhang were his advisors. 

Hierarchical model with normal + (missed it) + log + poisson


### 20 BC 10:30 am

#### Stephanie Kravitz


`r blogdown::shortcode("tweet", user="aaronquinlan", id="")`

`r blogdown::shortcode("tweet", user="aaronquinlan", id="")`

`r blogdown::shortcode("tweet", user="aaronquinlan", id="")`

`r blogdown::shortcode("tweet", user="aaronquinlan", id="")`


#### Li Chen


`r blogdown::shortcode("tweet", user="lcolladotor", id="")`

`r blogdown::shortcode("tweet", user="lcolladotor", id="")`

`r blogdown::shortcode("tweet", user="lcolladotor", id="")`


#### Nicholas Bogard


`r blogdown::shortcode("tweet", user="lcolladotor", id="")`

`r blogdown::shortcode("tweet", user="lcolladotor", id="")`


### Other


`r blogdown::shortcode("tweet", user="DaleYuzuki", id="")`

`r blogdown::shortcode("tweet", user="JEMgenes", id="")`

`r blogdown::shortcode("tweet", user="michaelhoffman", id="")`

`r blogdown::shortcode("tweet", user="averydavisbell", id="")`



### Diversity 


`r blogdown::shortcode("tweet", user="jsdron", id="")`

`r blogdown::shortcode("tweet", user="lcolladotor", id="")`

`r blogdown::shortcode("tweet", user="GeneticsSociety", id="")`

`r blogdown::shortcode("tweet", user="genome_sheriff", id="")`

`r blogdown::shortcode("tweet", user="SeymaKatrinli", id="")`

`r blogdown::shortcode("tweet", user="terencecwong", id="")`



### Misc


`r blogdown::shortcode("tweet", user="JansonWhite", id="")`

`r blogdown::shortcode("tweet", user="michaelhoffman", id="")`

`r blogdown::shortcode("tweet", user="aaronquinlan", id="")`

`r blogdown::shortcode("tweet", user="spendlove_sarah", id="")`

`r blogdown::shortcode("tweet", user="wouter_decoster", id="")`

`r blogdown::shortcode("tweet", user="apicoplast", id="")`

`r blogdown::shortcode("tweet", user="apicoplast", id="")`

`r blogdown::shortcode("tweet", user="genome_sheriff", id="")`


### The end

And that's a wrap!

`r blogdown::shortcode("tweet", user="cgonzagaj", id="")`

### Acknowledgments


This blog post was made possible thanks to:

* `r Biocpkg('BiocStyle')` `r citep(bib[['BiocStyle']])`
* `r CRANpkg('blogdown')` `r citep(bib[['blogdown']])`
* `r CRANpkg('knitcitations')` `r citep(bib[['knitcitations']])`
* `r CRANpkg('sessioninfo')` `r citep(bib[['sessioninfo']])`

### References

```{r bibliography, results = 'asis', echo = FALSE, cache = FALSE}
## Print bibliography
bibliography(style = 'html')
```

### Reproducibility

```{r reproducibility, echo = FALSE}
## Reproducibility info
options(width = 120)
session_info()
```
