---
title: ASHG18 tweet summary day 3
author: L. Collado-Torres
date: '2018-10-18'
slug: ashg18-tweet-summary-day-3
categories:
  - Conference
tags:
  - ASHG
header:
  caption: ''
  image: ''
  preview: yes
---

```{r setup, echo = FALSE, message = FALSE, warning = FALSE}
## For R images to display well in the RSS feed (disable for local preview)
knitr::opts_knit$set(base.url = 'http://lcolladotor.github.io/post/')

## Load frequently used packages for blog posts
library('knitcitations') # for citations
library('BiocStyle') # for CRANpkg() Biocpkg() Githubpkg()
library('sessioninfo') # for session_info()

## Load knitcitations with a clean bibliography
cleanbib()
cite_options(hyperlink = 'to.doc', citation_format = 'text', style = 'html')

bib <- c(
    'BiocStyle' = citation('BiocStyle'),
    'blogdown' = citation('blogdown')[2],
    'knitcitations' = citation('knitcitations'),
    'sessioninfo' = citation('sessioninfo')
)
```

Continuing from my [ASHG18 day 1 post](http://lcolladotor.github.io/2018/10/16/ashg18-tweet-summary-day-1/#.W8gWEBNKg0o) and [day 2](http://lcolladotor.github.io/2018/10/17/ashg18-tweet-summary-day-2/#.W8ggNxNKg0o), here's my list of tweets from day 3.


### 9:15 20BC

#### Jenna Carlson

`r blogdown::shortcode("tweet", user="CharlestonCWKC", id="1052956456578834432")`

`r blogdown::shortcode("tweet", user="StatGenDan", id="1052959881756430337")`


#### Christopher R. Gignoux


`r blogdown::shortcode("tweet", user="23andMeResearch", id="1052960113005215744")`

`r blogdown::shortcode("tweet", user="Brooke_LaFlamme", id="1052961594487988224")`

`r blogdown::shortcode("tweet", user="CharlestonCWKC", id="1052962128749969408")`

[www.pagestudy.org](www.pagestudy.org)

`r blogdown::shortcode("tweet", user="ElenaSorokin", id="1052962347810086913")`

#### Angela Andaleon

“It’s my pleasure to introduce to you Dr Angela Andaleon”
“Not a doctor yet!”
“Aspiring doctor Angela Andaleon”

^_^

Angela is presenting the continuation of her undergrad project. 


`r blogdown::shortcode("tweet", user="CharlestonCWKC", id="1052964260764995584")`

`r blogdown::shortcode("tweet", user="23andMeResearch", id="1052964989030490112")`


### 6C 10 am

#### Zongli Xu

`r blogdown::shortcode("tweet", user="michaelhoffman", id="1052968599705464832")`

#### Lang Wu


`r blogdown::shortcode("tweet", user="michaelhoffman", id="1052971499336781824")`

`r blogdown::shortcode("tweet", user="michaelhoffman", id="1052972239342133249")`

Hmm, why use a 0.01 $R^2$ cutoff? Isn’t that super low? Maybe I missed something. 

`r blogdown::shortcode("tweet", user="michaelhoffman", id="1052972394401263616")`

Moving to Hawaii to start his career as a PI. He had nice pictures to motivate others to join his lab ;)


### 11 am 6A

#### Hailiang Huang

Missed it: got there for the questions.

#### Tarjinder Singh

`r blogdown::shortcode("tweet", user="lcolladotor", id="1052991257847377921")`

They built a browser for seeing the rare variants and the exome data. Not available yet. 

#### Rujia Dai

`r blogdown::shortcode("tweet", user="lcolladotor", id="1052992420244156416")`

`r blogdown::shortcode("tweet", user="lcolladotor", id="1052993618246393856")`



#### Ying Ji

`r blogdown::shortcode("tweet", user="lcolladotor", id="1052995946051645440")`

`r blogdown::shortcode("tweet", user="lcolladotor", id="1052996602133008385")`


Bpred and Gpred genes have different expression over development: they intersect at birth. 

#### Kiran Girdhar

`r blogdown::shortcode("tweet", user="lcolladotor", id="1052998540669014016")`

`r blogdown::shortcode("tweet", user="lcolladotor", id="1053000456228622336")`

* Looked at enhancers too.
* Question from the audience about the differential shapes of the peaks between cases and controls. 
* Will look at QTLs after ASHG18. 


#### Siwei Zhang

Looked at SNPs associated with ATAC-seq data (ASoC ?). 

Used CRISPR to perturbe noncoding variants linked to SCZD risk: the ASoC SNPs. 

Then used single cell (10x Genomics) to measure expression. 


`r blogdown::shortcode("tweet", user="lcolladotor", id="1053003636135972864")`

### Other (morning)

`r blogdown::shortcode("tweet", user="anavinuela", id="1052999291764203521")`

`r blogdown::shortcode("tweet", user="StatGenDan", id="1053000619504500736")`

### Afternoon awards

#### Eric Lander

`r blogdown::shortcode("tweet", user="mycoacia", id="1053070553773293568")`

`r blogdown::shortcode("tweet", user="23andMeResearch", id="1053069188124762112")`

`r blogdown::shortcode("tweet", user="raungar", id="1053083099674755072")`

#### Jan M. Friedman

`r blogdown::shortcode("tweet", user="23andMeResearch", id="1053072202596147200")`

`r blogdown::shortcode("tweet", user="23andMeResearch", id="1053074190515941376")`

`r blogdown::shortcode("tweet", user="michaelhoffman", id="1053074247956946944")`

`r blogdown::shortcode("tweet", user="averydavisbell", id="1053075148725612544")`

### Presidential Symposium 

#### John Hawks

`r blogdown::shortcode("tweet", user="liminalphase", id="1053076488398888960")`

`r blogdown::shortcode("tweet", user="thatdnaguy", id="1053077309001891840")`

`r blogdown::shortcode("tweet", user="jlpcphotography", id="1053078045387444225")`

`r blogdown::shortcode("tweet", user="liminalphase", id="1053081405016571904")`

`r blogdown::shortcode("tweet", user="JHmeljak", id="1053083391711571969")`

#### Himla Soodyall

`r blogdown::shortcode("tweet", user="michaelhoffman", id="1053083269640540161")`

`r blogdown::shortcode("tweet", user="cgonzagaj", id="1053085462456221697")`

`r blogdown::shortcode("tweet", user="michaelhoffman", id="1053085978976432128")`

`r blogdown::shortcode("tweet", user="thatdnaguy", id="1053087721990672384")`

`r blogdown::shortcode("tweet", user="thatdnaguy", id="1053088764405272576")`

`r blogdown::shortcode("tweet", user="yhtacgnol", id="1053089547448287232")`

#### Ambroise Wonkman

`r blogdown::shortcode("tweet", user="michaelhoffman", id="1053090334236860416")`

`r blogdown::shortcode("tweet", user="GenomeBiology", id="1053090716551806976")`

### Diversity

`r blogdown::shortcode("tweet", user="sawerkar", id="1052956621477896192")`

`r blogdown::shortcode("tweet", user="Brooke_LaFlamme", id="1052968546945228801")`

`r blogdown::shortcode("tweet", user="tomsegal", id="1052970460089077764")`

Trolls :/

`r blogdown::shortcode("tweet", user="megkesh", id="1053002564181024768")`

`r blogdown::shortcode("tweet", user="yhtacgnol", id="1053091162372767744")`

### Misc


`r blogdown::shortcode("tweet", user="bioinfo_mark", id="1052964337197797376")`

`r blogdown::shortcode("tweet", user="Brooke_LaFlamme", id="1052964844381429761")`

This is hard. Some don’t mention the methods to avoid this issue, but then it becomes a “black box”. I guess that it can also be a “black box” if they don’t explain a bit what the model is/does. /shrug

`r blogdown::shortcode("tweet", user="genome_sheriff", id="1052970283533889536")`

`r blogdown::shortcode("tweet", user="alon_goren", id="1052990699166035968")`

`r blogdown::shortcode("tweet", user="ErickLoomis", id="1053000667969683458")`

`r blogdown::shortcode("tweet", user="dgmacarthur", id="1052996814356373504")`

`r blogdown::shortcode("tweet", user="hendricks_ae", id="1053073453035642881")`

`r blogdown::shortcode("tweet", user="johnomix", id="1053076114032205824")`

`r blogdown::shortcode("tweet", user="michaelhoffman", id="1053081242042691584")`



### Acknowledgments


This blog post was made possible thanks to:

* `r Biocpkg('BiocStyle')` `r citep(bib[['BiocStyle']])`
* `r CRANpkg('blogdown')` `r citep(bib[['blogdown']])`
* `r CRANpkg('knitcitations')` `r citep(bib[['knitcitations']])`
* `r CRANpkg('sessioninfo')` `r citep(bib[['sessioninfo']])`

and everyone that I met at the tweetup

`r blogdown::shortcode("tweet", user="michaelhoffman", id="1053167988109565952")`

`r blogdown::shortcode("tweet", user="meandertail", id="1053180338380333056")`

### References

```{r bibliography, results = 'asis', echo = FALSE, cache = FALSE}
## Print bibliography
bibliography(style = 'html')
```

### Reproducibility

```{r reproducibility, echo = FALSE}
## Reproducibility info
options(width = 120)
session_info()
```
