---
title: ASHG18 tweet summary day 2
author: L. Collado-Torres
date: '2018-10-17'
slug: ashg18-tweet-summary-day-2
categories:
  - Conference
tags:
  - ASHG
header:
  caption: ''
  image: ''
  preview: yes
---

```{r setup, echo = FALSE, message = FALSE, warning = FALSE}
## For R images to display well in the RSS feed (disable for local preview)
knitr::opts_knit$set(base.url = 'http://lcolladotor.github.io/post/')

## Load frequently used packages for blog posts
library('knitcitations') # for citations
library('BiocStyle') # for CRANpkg() Biocpkg() Githubpkg()
library('sessioninfo') # for session_info()

## Load knitcitations with a clean bibliography
cleanbib()
cite_options(hyperlink = 'to.doc', citation_format = 'text', style = 'html')

bib <- c(
    'BiocStyle' = citation('BiocStyle'),
    'blogdown' = citation('blogdown')[2],
    'knitcitations' = citation('knitcitations'),
    'sessioninfo' = citation('sessioninfo')
)
```


Continuing from my [ASHG18 day 1 post](http://lcolladotor.github.io/2018/10/16/ashg18-tweet-summary-day-1/#.W8gWEBNKg0o), here's my list of tweets from day 2. Note that I changed sessions a few times.


`r blogdown::shortcode("tweet", user="JulieNadel", id="1052618815274700802")`

`r blogdown::shortcode("tweet", user="dccc_phd", id="1052622201533358080")`
 

### 6E 10:30 am

`r blogdown::shortcode("tweet", user="NanibaaGarrison", id="1052077112931172352")`
 

#### Nanibaa’ Garrison 

`r blogdown::shortcode("tweet", user="lcolladotor", id="1052615800480129025")`

#### Maile Taualii

“Nobody wakes up thinking how can I harm indigenous populations!”

`r blogdown::shortcode("tweet", user="Brooke_LaFlamme", id="1052616982535667712")`

`r blogdown::shortcode("tweet", user="NanibaaGarrison", id="1052617666555338754")`

`r blogdown::shortcode("tweet", user="KeoluFox", id="1052617774818713601")`

`r blogdown::shortcode("tweet", user="Brooke_LaFlamme", id="1052618174028378112")`
 

#### Nadine Caron


`r blogdown::shortcode("tweet", user="CharlestonCWKC", id="1052618270384185345")`

`r blogdown::shortcode("tweet", user="johnhawks", id="1052618572575453185")`

`r blogdown::shortcode("tweet", user="lcolladotor", id="1052621619712090112")`

`r blogdown::shortcode("tweet", user="paleogenomics", id="1052622727578865665")`

`r blogdown::shortcode("tweet", user="popgenepi", id="1052621558194221056")`
 

#### Ngiare Brown

`r blogdown::shortcode("tweet", user="ElenaSorokin", id="1052622923918274565")`

`r blogdown::shortcode("tweet", user="riley_ilyse", id="1052623035084099587")`

`r blogdown::shortcode("tweet", user="NanibaaGarrison", id="1052624418856361984")`

Third time she mentioned “sexy research”. I thought that this term was frowned upon, maybe it's not.

#### Maui Hudson

He made us laugh with his conflict of interest slide. No commercial interests. Just interest in indigenous genomics and helping others. 

`r blogdown::shortcode("tweet", user="johnhawks", id="1052625563813339136")`

Issue with open data. They want to control how the data is re-used. Like for imputation: what are they looking at? Is it something they agree?


`r blogdown::shortcode("tweet", user="johnhawks", id="1052626680546758656")`

`r blogdown::shortcode("tweet", user="johnhawks", id="1052633878421274624")`

`r blogdown::shortcode("tweet", user="johnhawks", id="1052634541083512833")`
 


### 6C 11:30 am

#### Kelly East


`r blogdown::shortcode("tweet", user="girlscientist", id="1052628766739054592")`

`r blogdown::shortcode("tweet", user="averydavisbell", id="1052628958330552320")`

`r blogdown::shortcode("tweet", user="lcolladotor", id="1052630261052002304")`
 (others made better tweets!)


`r blogdown::shortcode("tweet", user="girlscientist", id="1052630028364599296")`

`r blogdown::shortcode("tweet", user="averydavisbell", id="1052630250918567937")`

`r blogdown::shortcode("tweet", user="sgpombe", id="1052631513332834304")`

`r blogdown::shortcode("tweet", user="averydavisbell", id="1052631235770572800")`

`r blogdown::shortcode("tweet", user="lcolladotor", id="1052631310290669568")`

`r blogdown::shortcode("tweet", user="lcolladotor", id="1052632738287706112")`

`r blogdown::shortcode("tweet", user="lcolladotor", id="1052633474354405377")`

I guess that it’s for US scientists, but I don't think of the "Deep South" in the US when I hear "SouthSeq". Anyway, SouthSeq looks like a great project with many ways to train others in genetics. 

“We are not going to run genetic providers out of jobs”. Loved this quote!


#### Chris Gunter

`r blogdown::shortcode("tweet", user="averydavisbell", id="1052636166804013056")`

35,000 page views on DNA awareness day3. 23andMe did a survey study in March 2018

`r blogdown::shortcode("tweet", user="MoleculeMind", id="1052636686025256960")`

`r blogdown::shortcode("tweet", user="CincyKidsGenomX", id="1052638967663800320")`

`r blogdown::shortcode("tweet", user="averydavisbell", id="1052639236086616065")`

`r blogdown::shortcode("tweet", user="lcolladotor", id="1052640088360796161")`

`r blogdown::shortcode("tweet", user="lcolladotor", id="1052641512524111872")`

`r blogdown::shortcode("tweet", user="yhtacgnol", id="1052641926833291264")`

`r blogdown::shortcode("tweet", user="lcolladotor", id="1052643639267012613")`

`r blogdown::shortcode("tweet", user="girlscientist", id="1052620297155829760")`
 

### Other (morning)

`r blogdown::shortcode("tweet", user="michaelhoffman", id="1052622463060701187")`

`r blogdown::shortcode("tweet", user="introspection", id="1052634348610977792")`
 

### 20BC 4:15 pm (4:23)

#### Semanti Mukherjee

`r blogdown::shortcode("tweet", user="michaelhoffman", id="1052701901886636032")`

`r blogdown::shortcode("tweet", user="Single_Molecule", id="1052701298502459392")`

`r blogdown::shortcode("tweet", user="cgonzagaj", id="1052702644764987392")`


#### Chimene Kesserwan:

`r blogdown::shortcode("tweet", user="michaelhoffman", id="1052704646773370880")`


#### Cynthia Zepeda

`r blogdown::shortcode("tweet", user="cgonzagaj", id="1052708167715414018")`

`r blogdown::shortcode("tweet", user="cgonzagaj", id="1052709637521166336")`


#### Xiaowu Gai

`r blogdown::shortcode("tweet", user="Single_Molecule", id="1052712645944532992")`

He thanked others for uploading data and making it publicly available so bioinformaticians like him can download it and re-analyze it. I totally agree with him!

### 6C 5:15 pm

#### Julio Barrera

Replaced by Chiba-Falek (lab PI).

Single cell (Neuron/glia)( ATAC-seq + RNA-seq + case-control data studying LOAD. RNA + ATAC matches.

#### Yungil Kim

PI Panos Roussos. Single cell data.

### Other (afternoon)

`r blogdown::shortcode("tweet", user="GenomeNathan", id="1052717804678303744")`

### 20 BC 6 pm

#### Christopher Lau

`r blogdown::shortcode("tweet", user="UDNconnect", id="1052726969597538304")`

`r blogdown::shortcode("tweet", user="lizworthey", id="1052729599803547648")`

#### Matt Velinder


`r blogdown::shortcode("tweet", user="lizworthey", id="1052732184937656321")`

`r blogdown::shortcode("tweet", user="lizworthey", id="1052732625134149632")`

`r blogdown::shortcode("tweet", user="lcolladotor", id="1052734223746908160")`


### 20 A 6:42 pm

#### Ira Hall

`r blogdown::shortcode("tweet", user="ryanlayer", id="1052736415744716800")`

Controlling for a nearby pLI gene? I’ve seen pLI mentioned a few times. Gotta read more about it!

### Sarcasm/fun

`r blogdown::shortcode("tweet", user="BiochemG_thall", id="1052625791853293569")`

`r blogdown::shortcode("tweet", user="ChloeReuterCGC", id="1052640703333859328")`

`r blogdown::shortcode("tweet", user="apicoplast", id="1052701624395649024")`

`r blogdown::shortcode("tweet", user="GenomeBiology", id="1052711607170621440")`

`r blogdown::shortcode("tweet", user="joyceykao", id="1052713384221716480")`
 plus they have a 50% off discount

`r blogdown::shortcode("tweet", user="apicoplast", id="1052715424859602944")`

`r blogdown::shortcode("tweet", user="genome_sheriff", id="1052727741668159488")`

### Diversity 

`r blogdown::shortcode("tweet", user="averydavisbell", id="1052716627689500672")`

`r blogdown::shortcode("tweet", user="NatalieTelis", id="1052717401429532672")`

`r blogdown::shortcode("tweet", user="lizworthey", id="1052720229715914753")`

### Motivational

`r blogdown::shortcode("tweet", user="skerfoot", id="1052629878569234432")`

### Acknowledgments


This blog post was made possible thanks to:

* `r Biocpkg('BiocStyle')` `r citep(bib[['BiocStyle']])`
* `r CRANpkg('blogdown')` `r citep(bib[['blogdown']])`
* `r CRANpkg('knitcitations')` `r citep(bib[['knitcitations']])`
* `r CRANpkg('sessioninfo')` `r citep(bib[['sessioninfo']])`

and everyone who wrote tweets with the [ASHG18](https://twitter.com/search?q=%23ASHG18) hashtag!

`r blogdown::shortcode("tweet", user="michaelhoffman", id="1051524651950718977")`

### References

```{r bibliography, results = 'asis', echo = FALSE, cache = FALSE}
## Print bibliography
bibliography(style = 'html')
```

### Reproducibility

```{r reproducibility, echo = FALSE}
## Reproducibility info
options(width = 120)
session_info()
```
