---
title: ASHG18 tweet summary day 1
author: L. Collado-Torres
date: '2018-10-16'
slug: ashg18-tweet-summary-day-1
categories:
  - Conference
tags:
  - ASHG
header:
  caption: ''
  image: ''
  preview: yes
---

```{r setup, echo = FALSE, message = FALSE, warning = FALSE}
## For R images to display well in the RSS feed (disable for local preview)
knitr::opts_knit$set(base.url = 'http://lcolladotor.github.io/post/')

## Load frequently used packages for blog posts
library('knitcitations') # for citations
library('BiocStyle') # for CRANpkg() Biocpkg() Githubpkg()
library('sessioninfo') # for session_info()

## Load knitcitations with a clean bibliography
cleanbib()
cite_options(hyperlink = 'to.doc', citation_format = 'text', style = 'html')

bib <- c(
    'BiocStyle' = citation('BiocStyle'),
    'blogdown' = citation('blogdown')[2],
    'knitcitations' = citation('knitcitations'),
    'sessioninfo' = citation('sessioninfo')
)
```

Today was the first day of the [American Society of Human Genetics (ASHG) 2018 conference](http://www.ashg.org/2018meeting/). The official hashtag for the conference is [ASHG18](https://twitter.com/search?q=%23ASHG18) on Twitter. At first I was tweeting myself and checking both the _top_ and the _latest_ tweets. As the day progressed I started a Google Doc to take notes during talks. I was missing some details so I was relying on the _latest_ tweets and copy-pasting the tweet links to my notes. At some point I told myself I should simply turn this collection of tweet links into a simple blog post. So here it is for day 1. You can consider it a curated list of the [ASHG18](https://twitter.com/search?q=%23ASHG18) tweets. Although it's incomplete because it only covers the talks I went to starting from the Presidential address. 

The linked tweets are frequently from [Eli Robertson](https://twitter.com/thatdnaguy)^[Eli Robertson creates great Twitter threads, so I frequently only link to the first tweet of the thread.] and [Michael Hoffmann](https://twitter.com/michaelhoffman)^[Michael Hoffmann also writes multiple tweets per talk, though you'll have to scroll through his timeline to find all the ones related to a talk. Unless I'm missing a way to make them into a thread.], but also from other Twitter users^[Some with a few followers, some with many. It didn't matter. I was just checking the _latest_ and saving the ones I liked the most.].

So, without further ado, here we go:

`r blogdown::shortcode("tweet", user="skathire", id="")`

### Award presentations

`r blogdown::shortcode("tweet", user="michaelhoffman", id="")`

Sek also thanked all his mentees ^^.

`r blogdown::shortcode("tweet", user="thatdnaguy", id="")`

`r blogdown::shortcode("tweet", user="MariaChahrour", id="")`

### Diversity

`r blogdown::shortcode("tweet", user="michaelhoffman", id="")`

`r blogdown::shortcode("tweet", user="princyparsana", id="")`

`r blogdown::shortcode("tweet", user="lcolladotor", id="")`

`r blogdown::shortcode("tweet", user="lcolladotor", id="")`

`r blogdown::shortcode("tweet", user="lcolladotor", id="")`

### Mitchel Cole

SNP crispr-cas9 perturbation study in blood cells.

`r blogdown::shortcode("tweet", user="thatdnaguy", id="")`

`r blogdown::shortcode("tweet", user="aidanbutty", id="")`

MC mentioned metaFDR for combining pvalues from 4 tests.


### Priyanka Nakka

Uniparental disomy using 23andMe data. Seeking prevalence information in general population.

`r blogdown::shortcode("tweet", user="thatdnaguy", id="")`

`r blogdown::shortcode("tweet", user="michaelhoffman", id="")`

3 types that can be identified by 2 in silico methods.

`r blogdown::shortcode("tweet", user="CharlestonCWKC", id="")`

`r blogdown::shortcode("tweet", user="23andMeResearch", id="")`

`r blogdown::shortcode("tweet", user="23andMeResearch", id="")`

`r blogdown::shortcode("tweet", user="thatdnaguy", id="")`

Mentioned PheWAS. 

PN: Don't know if you can get single cell data from 23andMe customers.


`r blogdown::shortcode("tweet", user="23andMeResearch", id="")`

`r blogdown::shortcode("tweet", user="beryl_bbc", id="")`

`r blogdown::shortcode("tweet", user="s_ramach", id="")`


### Jack A Kosmicki

`r blogdown::shortcode("tweet", user="beryl_bbc", id="")`

`r blogdown::shortcode("tweet", user="thatdnaguy", id="")`



mentioned pLl method 

`r blogdown::shortcode("tweet", user="DrGeneUK", id="")`

`r blogdown::shortcode("tweet", user="Single_Molecule", id="")`

`r blogdown::shortcode("tweet", user="ksamocha", id="")`


99 ASD genes 

`r blogdown::shortcode("tweet", user="beryl_bbc", id="")`

`r blogdown::shortcode("tweet", user="michaelhoffman", id="")`

summary

`r blogdown::shortcode("tweet", user="StatGenDan", id="")`

`r blogdown::shortcode("tweet", user="thatdnaguy", id="")`

### Caitlin Bowen

`r blogdown::shortcode("tweet", user="thatdnaguy", id="")`

Sorry, I left this talk early to see the poster talks (that I didn't know had been delayed).


### Wrap up

`r blogdown::shortcode("tweet", user="thatdnaguy", id="")`

### Poster talks

`r blogdown::shortcode("tweet", user="Genomes2People", id="")`

Single cell composition and organs poster 2012 seemed interesting to me. I added to my calendar!



### Acknowledgments

This blog post was made possible thanks to:

* `r Biocpkg('BiocStyle')` `r citep(bib[['BiocStyle']])`
* `r CRANpkg('blogdown')` `r citep(bib[['blogdown']])`
* `r CRANpkg('knitcitations')` `r citep(bib[['knitcitations']])`
* `r CRANpkg('sessioninfo')` `r citep(bib[['sessioninfo']])`

as well as everyone who was tweeting! See you on Thursday!

`r blogdown::shortcode("tweet", user="michaelhoffman", id="")`

### References

```{r bibliography, results = 'asis', echo = FALSE, cache = FALSE}
## Print bibliography
bibliography(style = 'html')
```

### Reproducibility

```{r reproducibility, echo = FALSE}
## Reproducibility info
options(width = 120)
session_info()
```
