---
title: ASHG18 tweet summary day 2
author: L. Collado-Torres
date: '2018-10-17'
slug: ashg18-tweet-summary-day-2
categories:
  - Conference
tags:
  - ASHG
header:
  caption: ''
  image: ''
  preview: yes
---

```{r setup, echo = FALSE, message = FALSE, warning = FALSE}
## For R images to display well in the RSS feed (disable for local preview)
knitr::opts_knit$set(base.url = 'http://lcolladotor.github.io/post/')

## Load frequently used packages for blog posts
library('knitcitations') # for citations
library('BiocStyle') # for CRANpkg() Biocpkg() Githubpkg()
library('sessioninfo') # for session_info()

## Load knitcitations with a clean bibliography
cleanbib()
cite_options(hyperlink = 'to.doc', citation_format = 'text', style = 'html')

bib <- c(
    'BiocStyle' = citation('BiocStyle'),
    'blogdown' = citation('blogdown')[2],
    'knitcitations' = citation('knitcitations'),
    'sessioninfo' = citation('sessioninfo')
)
```


Continuing from my [ASHG18 day 1 post](http://lcolladotor.github.io/2018/10/16/ashg18-tweet-summary-day-1/#.W8gWEBNKg0o), here's my list of tweets from day 2. Note that I changed sessions a few times.


`r blogdown::shortcode("tweet", user="JulieNadel", id="")`

`r blogdown::shortcode("tweet", user="dccc_phd", id="")`
 

### 6E 10:30 am

`r blogdown::shortcode("tweet", user="NanibaaGarrison", id="")`
 

#### Nanibaa’ Garrison 

`r blogdown::shortcode("tweet", user="lcolladotor", id="")`

#### Maile Taualii

“Nobody wakes up thinking how can I harm indigenous populations!”

`r blogdown::shortcode("tweet", user="Brooke_LaFlamme", id="")`

`r blogdown::shortcode("tweet", user="NanibaaGarrison", id="")`

`r blogdown::shortcode("tweet", user="KeoluFox", id="")`

`r blogdown::shortcode("tweet", user="Brooke_LaFlamme", id="")`
 

#### Nadine Caron


`r blogdown::shortcode("tweet", user="CharlestonCWKC", id="")`

`r blogdown::shortcode("tweet", user="johnhawks", id="")`

`r blogdown::shortcode("tweet", user="lcolladotor", id="")`

`r blogdown::shortcode("tweet", user="paleogenomics", id="")`

`r blogdown::shortcode("tweet", user="popgenepi", id="")`
 

#### Ngiare Brown

`r blogdown::shortcode("tweet", user="ElenaSorokin", id="")`

`r blogdown::shortcode("tweet", user="riley_ilyse", id="")`

`r blogdown::shortcode("tweet", user="NanibaaGarrison", id="")`

Third time she mentioned “sexy research”. I thought that this term was frowned upon, maybe it's not.

#### Maui Hudson

He made us laugh with his conflict of interest slide. No commercial interests. Just interest in indigenous genomics and helping others. 

`r blogdown::shortcode("tweet", user="johnhawks", id="")`

Issue with open data. They want to control how the data is re-used. Like for imputation: what are they looking at? Is it something they agree?


`r blogdown::shortcode("tweet", user="johnhawks", id="")`

`r blogdown::shortcode("tweet", user="johnhawks", id="")`

`r blogdown::shortcode("tweet", user="johnhawks", id="")`
 


### 6C 11:30 am

#### Kelly East


`r blogdown::shortcode("tweet", user="girlscientist", id="")`

`r blogdown::shortcode("tweet", user="averydavisbell", id="")`

`r blogdown::shortcode("tweet", user="lcolladotor", id="")`
 (others made better tweets!)


`r blogdown::shortcode("tweet", user="girlscientist", id="")`

`r blogdown::shortcode("tweet", user="averydavisbell", id="")`

`r blogdown::shortcode("tweet", user="sgpombe", id="")`

`r blogdown::shortcode("tweet", user="averydavisbell", id="")`

`r blogdown::shortcode("tweet", user="lcolladotor", id="")`

`r blogdown::shortcode("tweet", user="lcolladotor", id="")`

`r blogdown::shortcode("tweet", user="lcolladotor", id="")`

I guess that it’s for US scientists, but I don't think of the "Deep South" in the US when I hear "SouthSeq". Anyway, SouthSeq looks like a great project with many ways to train others in genetics. 

“We are not going to run genetic providers out of jobs”. Loved this quote!


#### Chris Gunter

`r blogdown::shortcode("tweet", user="averydavisbell", id="")`

35,000 page views on DNA awareness day3. 23andMe did a survey study in March 2018

`r blogdown::shortcode("tweet", user="MoleculeMind", id="")`

`r blogdown::shortcode("tweet", user="CincyKidsGenomX", id="")`

`r blogdown::shortcode("tweet", user="averydavisbell", id="")`

`r blogdown::shortcode("tweet", user="lcolladotor", id="")`

`r blogdown::shortcode("tweet", user="lcolladotor", id="")`

`r blogdown::shortcode("tweet", user="yhtacgnol", id="")`

`r blogdown::shortcode("tweet", user="lcolladotor", id="")`

`r blogdown::shortcode("tweet", user="girlscientist", id="")`
 

### Other (morning)

`r blogdown::shortcode("tweet", user="michaelhoffman", id="")`

`r blogdown::shortcode("tweet", user="introspection", id="")`
 

### 20BC 4:15 pm (4:23)

#### Semanti Mukherjee

`r blogdown::shortcode("tweet", user="michaelhoffman", id="")`

`r blogdown::shortcode("tweet", user="Single_Molecule", id="")`

`r blogdown::shortcode("tweet", user="cgonzagaj", id="")`


#### Chimene Kesserwan:

`r blogdown::shortcode("tweet", user="michaelhoffman", id="")`


#### Cynthia Zepeda

`r blogdown::shortcode("tweet", user="cgonzagaj", id="")`

`r blogdown::shortcode("tweet", user="cgonzagaj", id="")`


#### Xiaowu Gai

`r blogdown::shortcode("tweet", user="Single_Molecule", id="")`

He thanked others for uploading data and making it publicly available so bioinformaticians like him can download it and re-analyze it. I totally agree with him!

### 6C 5:15 pm

#### Julio Barrera

Replaced by Chiba-Falek (lab PI).

Single cell (Neuron/glia)( ATAC-seq + RNA-seq + case-control data studying LOAD. RNA + ATAC matches.

#### Yungil Kim

PI Panos Roussos. Single cell data.

### Other (afternoon)

`r blogdown::shortcode("tweet", user="GenomeNathan", id="")`

### 20 BC 6 pm

#### Christopher Lau

`r blogdown::shortcode("tweet", user="UDNconnect", id="")`

`r blogdown::shortcode("tweet", user="lizworthey", id="")`

#### Matt Velinder


`r blogdown::shortcode("tweet", user="lizworthey", id="")`

`r blogdown::shortcode("tweet", user="lizworthey", id="")`

`r blogdown::shortcode("tweet", user="lcolladotor", id="")`


### 20 A 6:42 pm

#### Ira Hall

`r blogdown::shortcode("tweet", user="ryanlayer", id="")`

Controlling for a nearby pLI gene? I’ve seen pLI mentioned a few times. Gotta read more about it!

### Sarcasm/fun

`r blogdown::shortcode("tweet", user="BiochemG_thall", id="")`

`r blogdown::shortcode("tweet", user="ChloeReuterCGC", id="")`

`r blogdown::shortcode("tweet", user="apicoplast", id="")`

`r blogdown::shortcode("tweet", user="GenomeBiology", id="")`

`r blogdown::shortcode("tweet", user="joyceykao", id="")`
 plus they have a 50% off discount

`r blogdown::shortcode("tweet", user="apicoplast", id="")`

`r blogdown::shortcode("tweet", user="genome_sheriff", id="")`

### Diversity 

`r blogdown::shortcode("tweet", user="averydavisbell", id="")`

`r blogdown::shortcode("tweet", user="NatalieTelis", id="")`

`r blogdown::shortcode("tweet", user="lizworthey", id="")`

### Motivational

`r blogdown::shortcode("tweet", user="skerfoot", id="")`

### Acknowledgments


This blog post was made possible thanks to:

* `r Biocpkg('BiocStyle')` `r citep(bib[['BiocStyle']])`
* `r CRANpkg('blogdown')` `r citep(bib[['blogdown']])`
* `r CRANpkg('knitcitations')` `r citep(bib[['knitcitations']])`
* `r CRANpkg('sessioninfo')` `r citep(bib[['sessioninfo']])`

and everyone who wrote tweets with the [ASHG18](https://twitter.com/search?q=%23ASHG18) hashtag!

`r blogdown::shortcode("tweet", user="michaelhoffman", id="")`

### References

```{r bibliography, results = 'asis', echo = FALSE, cache = FALSE}
## Print bibliography
bibliography(style = 'html')
```

### Reproducibility

```{r reproducibility, echo = FALSE}
## Reproducibility info
options(width = 120)
session_info()
```
