---
title: ASHG18 tweet summary day 4
author: L. Collado-Torres
date: '2018-10-19'
slug: ashg18-tweet-summary-day-4
categories:
  - Conference
tags:
  - ASHG
header:
  caption: ''
  image: ''
  preview: yes
---

```{r setup, echo = FALSE, message = FALSE, warning = FALSE}
## For R images to display well in the RSS feed (disable for local preview)
knitr::opts_knit$set(base.url = 'http://lcolladotor.github.io/post/')

## Load frequently used packages for blog posts
library('knitcitations') # for citations
library('BiocStyle') # for CRANpkg() Biocpkg() Githubpkg()
library('sessioninfo') # for session_info()

## Load knitcitations with a clean bibliography
cleanbib()
cite_options(hyperlink = 'to.doc', citation_format = 'text', style = 'html')

bib <- c(
    'BiocStyle' = citation('BiocStyle'),
    'blogdown' = citation('blogdown')[2],
    'knitcitations' = citation('knitcitations'),
    'sessioninfo' = citation('sessioninfo')
)
```

Continuing from my [ASHG18 day 1 post](http://lcolladotor.github.io/2018/10/16/ashg18-tweet-summary-day-1/#.W8gWEBNKg0o), [day 2](http://lcolladotor.github.io/2018/10/17/ashg18-tweet-summary-day-2/#.W8ggNxNKg0o), [day 3](http://lcolladotor.github.io/2018/10/18/ashg18-tweet-summary-day-3/#.W8mYLxNKg0o) here's my list of tweets from day 4.

### 6F 11:00 am

#### Cecilia Lingdren

Got there at the end :P

Had #diversitymatters and many flags including the rainbow one in her last slide. 

#### Benjamin Neale

`r blogdown::shortcode("tweet", "1053356294369759233")`

`r blogdown::shortcode("tweet", "1053356661694324736")`

`r blogdown::shortcode("tweet", "1053356800609705984")`

`r blogdown::shortcode("tweet", "1053360343408246784")`


All results are available to download for free from his lab website!

#### Barbara Stranger

`r blogdown::shortcode("tweet", "1053369322981085184")`


### Other (morning)


`r blogdown::shortcode("tweet", "1053319220048486400")`

`r blogdown::shortcode("tweet", "1053320618194522113")`

`r blogdown::shortcode("tweet", "1053324083771789313")`

`r blogdown::shortcode("tweet", "1053358670925316096")`

`r blogdown::shortcode("tweet", "1053363725376282624")`

### Afternoon


`r blogdown::shortcode("tweet", "1053427841029693440")`

`r blogdown::shortcode("tweet", "1053428153857728512")`

`r blogdown::shortcode("tweet", "1053429511604195328")`

`r blogdown::shortcode("tweet", "1053429846821429249")`

`r blogdown::shortcode("tweet", "1053433460721836032")`

`r blogdown::shortcode("tweet", "1053432233610989568")`

`r blogdown::shortcode("tweet", "1053429016739241984")`


### Diversity


`r blogdown::shortcode("tweet", "1053322523973013504")`

`r blogdown::shortcode("tweet", "1053363947154243584")`

`r blogdown::shortcode("tweet", "1053365583566188544")`

`r blogdown::shortcode("tweet", "1053367064168022016")`

### Misc


`r blogdown::shortcode("tweet", "1053320504122036224")`

`r blogdown::shortcode("tweet", "1053320437814325248")`

`r blogdown::shortcode("tweet", "1053353588146155520")`

`r blogdown::shortcode("tweet", "1053356648247418881")`

`r blogdown::shortcode("tweet", "1053358887737442305")`

`r blogdown::shortcode("tweet", "1053365107235807233")`

`r blogdown::shortcode("tweet", "1053434810150993921")`


### Acknowledgements


This blog post was made possible thanks to:

* `r Biocpkg('BiocStyle')` `r citep(bib[['BiocStyle']])`
* `r CRANpkg('blogdown')` `r citep(bib[['blogdown']])`
* `r CRANpkg('knitcitations')` `r citep(bib[['knitcitations']])`
* `r CRANpkg('sessioninfo')` `r citep(bib[['sessioninfo']])`

### References

```{r bibliography, results = 'asis', echo = FALSE, cache = FALSE}
## Print bibliography
bibliography(style = 'html')
```

### Reproducibility

```{r reproducibility, echo = FALSE}
## Reproducibility info
options(width = 120)
session_info()
```
