---
title: ASHG18 tweet summary day 5
author: L. Collado-Torres
date: '2018-10-20'
slug: ashg18-tweet-summary-day-5
categories:
  - Conference
tags:
  - ASHG
header:
  caption: ''
  image: ''
  preview: yes
---

```{r setup, echo = FALSE, message = FALSE, warning = FALSE}
## For R images to display well in the RSS feed (disable for local preview)
knitr::opts_knit$set(base.url = 'http://lcolladotor.github.io/post/')

## Load frequently used packages for blog posts
library('knitcitations') # for citations
library('BiocStyle') # for CRANpkg() Biocpkg() Githubpkg()
library('sessioninfo') # for session_info()

## Load knitcitations with a clean bibliography
cleanbib()
cite_options(hyperlink = 'to.doc', citation_format = 'text', style = 'html')

bib <- c(
    'BiocStyle' = citation('BiocStyle'),
    'blogdown' = citation('blogdown')[2],
    'knitcitations' = citation('knitcitations'),
    'sessioninfo' = citation('sessioninfo')
)
```


Continuing from my [ASHG18 day 1 post](http://lcolladotor.github.io/2018/10/16/ashg18-tweet-summary-day-1/#.W8gWEBNKg0o), [day 2](http://lcolladotor.github.io/2018/10/17/ashg18-tweet-summary-day-2/#.W8ggNxNKg0o), [day 3](http://lcolladotor.github.io/2018/10/18/ashg18-tweet-summary-day-3/#.W8mYLxNKg0o) and [day4](http://lcolladotor.github.io/2018/10/19/ashg18-tweet-summary-day-4/#.W8qdTRNKg0o) here's my list of tweets from day 5.

### 6C 9:15 am

#### Jane Loveland


`r blogdown::shortcode("tweet", "1053673447040184320")`

`r blogdown::shortcode("tweet", "1053682492316672001")`

`r blogdown::shortcode("tweet", "1053683827359404034")`

`r blogdown::shortcode("tweet", "1053684796398817280")`

`r blogdown::shortcode("tweet", "1053685569027330048")`



### 6B 10 am

#### Genevieve Stein-O’Brien

`r blogdown::shortcode("tweet", "1053693765007724544")`

#### Yu Hu

`r blogdown::shortcode("tweet", "1053699063990734848")`

Mingyao Li and Nancy Zhang were his advisors. 

Hierarchical model with normal + (missed it) + log + poisson


### 20 BC 10:30 am

#### Stephanie Kravitz


`r blogdown::shortcode("tweet", "1053700571121610752")`

`r blogdown::shortcode("tweet", "1053700970616504320")`

`r blogdown::shortcode("tweet", "1053702240412651521")`

`r blogdown::shortcode("tweet", "1053703467091423232")`


#### Li Chen


`r blogdown::shortcode("tweet", "1053705292880310273")`

`r blogdown::shortcode("tweet", "1053706299051925504")`

`r blogdown::shortcode("tweet", "1053708045170032640")`


#### Nicholas Bogard


`r blogdown::shortcode("tweet", "1053709703916580865")`

`r blogdown::shortcode("tweet", "1053711826813280256")`


### Other


`r blogdown::shortcode("tweet", "1053674723970813952")`

`r blogdown::shortcode("tweet", "1053693658518642688")`

`r blogdown::shortcode("tweet", "1053697490124386304")`

`r blogdown::shortcode("tweet", "1053709216878194688")`



### Diversity 


`r blogdown::shortcode("tweet", "1053674078966493184")`

`r blogdown::shortcode("tweet", "1053677254260088834")`

`r blogdown::shortcode("tweet", "1053681995912368128")`

`r blogdown::shortcode("tweet", "1053707734288261120")`

`r blogdown::shortcode("tweet", "1053682864301105152")`

`r blogdown::shortcode("tweet", "1053686351789346818")`



### Misc


`r blogdown::shortcode("tweet", "1053684376679010305")`

`r blogdown::shortcode("tweet", "1053693247418073088")`

`r blogdown::shortcode("tweet", "1053698711216214016")`

`r blogdown::shortcode("tweet", "1053699388881592320")`

`r blogdown::shortcode("tweet", "1053704802549428225")`

`r blogdown::shortcode("tweet", "1053707539844521984")`

`r blogdown::shortcode("tweet", "1053708117576306690")`

`r blogdown::shortcode("tweet", "1053710100811018240")`


### The end

And that's a wrap!

`r blogdown::shortcode("tweet", "1053716471962992641")`

### Acknowledgements


This blog post was made possible thanks to:

* `r Biocpkg('BiocStyle')` `r citep(bib[['BiocStyle']])`
* `r CRANpkg('blogdown')` `r citep(bib[['blogdown']])`
* `r CRANpkg('knitcitations')` `r citep(bib[['knitcitations']])`
* `r CRANpkg('sessioninfo')` `r citep(bib[['sessioninfo']])`

### References

```{r bibliography, results = 'asis', echo = FALSE, cache = FALSE}
## Print bibliography
bibliography(style = 'html')
```

### Reproducibility

```{r reproducibility, echo = FALSE}
## Reproducibility info
options(width = 120)
session_info()
```
