---
title: ASHG18 tweet summary day 3
author: L. Collado-Torres
date: '2018-10-18'
slug: ashg18-tweet-summary-day-3
categories:
  - Conference
tags:
  - ASHG
header:
  caption: ''
  image: ''
  preview: yes
---

```{r setup, echo = FALSE, message = FALSE, warning = FALSE}
## For R images to display well in the RSS feed (disable for local preview)
knitr::opts_knit$set(base.url = 'http://lcolladotor.github.io/post/')

## Load frequently used packages for blog posts
library('knitcitations') # for citations
library('BiocStyle') # for CRANpkg() Biocpkg() Githubpkg()
library('sessioninfo') # for session_info()

## Load knitcitations with a clean bibliography
cleanbib()
cite_options(hyperlink = 'to.doc', citation_format = 'text', style = 'html')

bib <- c(
    'BiocStyle' = citation('BiocStyle'),
    'blogdown' = citation('blogdown')[2],
    'knitcitations' = citation('knitcitations'),
    'sessioninfo' = citation('sessioninfo')
)
```

Continuing from my [ASHG18 day 1 post](http://lcolladotor.github.io/2018/10/16/ashg18-tweet-summary-day-1/#.W8gWEBNKg0o) and [day 2](http://lcolladotor.github.io/2018/10/17/ashg18-tweet-summary-day-2/#.W8ggNxNKg0o), here's my list of tweets from day 3.


### 9:15 20BC

#### Jenna Carlson

`r blogdown::shortcode("tweet", user="CharlestonCWKC", id="")`

`r blogdown::shortcode("tweet", user="StatGenDan", id="")`


#### Christopher R. Gignoux


`r blogdown::shortcode("tweet", user="23andMeResearch", id="")`

`r blogdown::shortcode("tweet", user="Brooke_LaFlamme", id="")`

`r blogdown::shortcode("tweet", user="CharlestonCWKC", id="")`

[www.pagestudy.org](www.pagestudy.org)

`r blogdown::shortcode("tweet", user="ElenaSorokin", id="")`

#### Angela Andaleon

“It’s my pleasure to introduce to you Dr Angela Andaleon”
“Not a doctor yet!”
“Aspiring doctor Angela Andaleon”

^_^

Angela is presenting the continuation of her undergrad project. 


`r blogdown::shortcode("tweet", user="CharlestonCWKC", id="")`

`r blogdown::shortcode("tweet", user="23andMeResearch", id="")`


### 6C 10 am

#### Zongli Xu

`r blogdown::shortcode("tweet", user="michaelhoffman", id="")`

#### Lang Wu


`r blogdown::shortcode("tweet", user="michaelhoffman", id="")`

`r blogdown::shortcode("tweet", user="michaelhoffman", id="")`

Hmm, why use a 0.01 $R^2$ cutoff? Isn’t that super low? Maybe I missed something. 

`r blogdown::shortcode("tweet", user="michaelhoffman", id="")`

Moving to Hawaii to start his career as a PI. He had nice pictures to motivate others to join his lab ;)


### 11 am 6A

#### Hailiang Huang

Missed it: got there for the questions.

#### Tarjinder Singh

`r blogdown::shortcode("tweet", user="lcolladotor", id="")`

They built a browser for seeing the rare variants and the exome data. Not available yet. 

#### Rujia Dai

`r blogdown::shortcode("tweet", user="lcolladotor", id="")`

`r blogdown::shortcode("tweet", user="lcolladotor", id="")`



#### Ying Ji

`r blogdown::shortcode("tweet", user="lcolladotor", id="")`

`r blogdown::shortcode("tweet", user="lcolladotor", id="")`


Bpred and Gpred genes have different expression over development: they intersect at birth. 

#### Kiran Girdhar

`r blogdown::shortcode("tweet", user="lcolladotor", id="")`

`r blogdown::shortcode("tweet", user="lcolladotor", id="")`

* Looked at enhancers too.
* Question from the audience about the differential shapes of the peaks between cases and controls. 
* Will look at QTLs after ASHG18. 


#### Siwei Zhang

Looked at SNPs associated with ATAC-seq data (ASoC ?). 

Used CRISPR to perturbe noncoding variants linked to SCZD risk: the ASoC SNPs. 

Then used single cell (10x Genomics) to measure expression. 


`r blogdown::shortcode("tweet", user="lcolladotor", id="")`

### Other (morning)

`r blogdown::shortcode("tweet", user="Single_Molecule", id="")`

`r blogdown::shortcode("tweet", user="anavinuela", id="")`

`r blogdown::shortcode("tweet", user="StatGenDan", id="")`

### Afternoon awards

#### Eric Lander

`r blogdown::shortcode("tweet", user="mycoacia", id="")`

`r blogdown::shortcode("tweet", user="23andMeResearch", id="")`

`r blogdown::shortcode("tweet", user="raungar", id="")`

#### Jan M. Friedman

`r blogdown::shortcode("tweet", user="23andMeResearch", id="")`

`r blogdown::shortcode("tweet", user="23andMeResearch", id="")`

`r blogdown::shortcode("tweet", user="michaelhoffman", id="")`

`r blogdown::shortcode("tweet", user="averydavisbell", id="")`

### Presidential Symposium 

#### John Hawks

`r blogdown::shortcode("tweet", user="liminalphase", id="")`

`r blogdown::shortcode("tweet", user="thatdnaguy", id="")`

`r blogdown::shortcode("tweet", user="jlpcphotography", id="")`

`r blogdown::shortcode("tweet", user="liminalphase", id="")`

`r blogdown::shortcode("tweet", user="JHmeljak", id="")`

#### Himla Soodyall

`r blogdown::shortcode("tweet", user="michaelhoffman", id="")`

`r blogdown::shortcode("tweet", user="cgonzagaj", id="")`

`r blogdown::shortcode("tweet", user="michaelhoffman", id="")`

`r blogdown::shortcode("tweet", user="thatdnaguy", id="")`

`r blogdown::shortcode("tweet", user="thatdnaguy", id="")`

`r blogdown::shortcode("tweet", user="yhtacgnol", id="")`

#### Ambroise Wonkman

`r blogdown::shortcode("tweet", user="michaelhoffman", id="")`

`r blogdown::shortcode("tweet", user="GenomeBiology", id="")`

### Diversity

`r blogdown::shortcode("tweet", user="sawerkar", id="")`

`r blogdown::shortcode("tweet", user="Brooke_LaFlamme", id="")`

`r blogdown::shortcode("tweet", user="tomsegal", id="")`

Trolls :/

`r blogdown::shortcode("tweet", user="megkesh", id="")`

`r blogdown::shortcode("tweet", user="yhtacgnol", id="")`

### Misc


`r blogdown::shortcode("tweet", user="bioinfo_mark", id="")`

`r blogdown::shortcode("tweet", user="Brooke_LaFlamme", id="")`

This is hard. Some don’t mention the methods to avoid this issue, but then it becomes a “black box”. I guess that it can also be a “black box” if they don’t explain a bit what the model is/does. /shrug

`r blogdown::shortcode("tweet", user="genome_sheriff", id="")`

`r blogdown::shortcode("tweet", user="alon_goren", id="")`

`r blogdown::shortcode("tweet", user="ErickLoomis", id="")`

`r blogdown::shortcode("tweet", user="dgmacarthur", id="")`

`r blogdown::shortcode("tweet", user="hendricks_ae", id="")`

`r blogdown::shortcode("tweet", user="johnomix", id="")`

`r blogdown::shortcode("tweet", user="michaelhoffman", id="")`



### Acknowledgments


This blog post was made possible thanks to:

* `r Biocpkg('BiocStyle')` `r citep(bib[['BiocStyle']])`
* `r CRANpkg('blogdown')` `r citep(bib[['blogdown']])`
* `r CRANpkg('knitcitations')` `r citep(bib[['knitcitations']])`
* `r CRANpkg('sessioninfo')` `r citep(bib[['sessioninfo']])`

and everyone that I met at the tweetup

`r blogdown::shortcode("tweet", user="michaelhoffman", id="")`

`r blogdown::shortcode("tweet", user="meandertail", id="")`

### References

```{r bibliography, results = 'asis', echo = FALSE, cache = FALSE}
## Print bibliography
bibliography(style = 'html')
```

### Reproducibility

```{r reproducibility, echo = FALSE}
## Reproducibility info
options(width = 120)
session_info()
```
